APPM report - Draft

### 2022-10-24 paper_version/main.tex
polish until 3d full scheme

\newtheorem*{remark}{Remark}

@@

\title{APPM report - Draft}
\author[1]{R. Hiptmair}
\author[1]{T.W. Yu}
\author[2]{R. Fuchs}
\affil[1]{Seminar for Applied Mathematics , ETH Z\"{u}rich}
\affil[2]{IET Institut für Energietechnik, OST}
\date{}
\begin{document}
\maketitle

@@

\section{Spatial Discretization}
\subsection{Primal-dual Staggered Meshes}
\subsubsection{Geometric Property}
Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use. The spatial domain is discretized by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively. The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered.

@@

The orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.

@@

\begin{figure}
    \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \resizebox{0.45\textwidth}{!}{\begin{tikzpicture}
    \def\primalstyle{thick}
    \def\dualstyle{ultra thick}
    \coordinate (P0) at (0cm, 0cm);
    \foreach \i in {1,2,...,6}
    {
    \coordinate (P\i) at ({60*\i-30}:2cm);
    \draw[\primalstyle] (P0) -- (P\i);
    }
    \draw[\primalstyle] (P1) -- (P2) node[above=3mm]{\Large $\mathcal{M}$} node[left=11mm]{\Large \color{blue} $\Tilde{\mathcal{M}}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
    \foreach \i in {1,2,...,6}
    {
    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
    \coordinate (DD\i) at ({60*\i-60}:{4./1.737});
    }
    \draw[blue,\dualstyle] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
    \foreach \i in {1,2,...,6}
    {
    \draw[blue,\dualstyle] (D\i) -- (DD\i);
    }
    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
    \end{tikzpicture}}
    \caption{2D case}
    \label{fig:2d-mesh}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \resizebox{0.8\textwidth}{!}{\begin{tikzpicture}
    \def\primalstyle{thick}
    \def\dualstyle{thick}
    \coordinate (P0) at (0cm, 0cm);
    \foreach \i in {1,2,...,6}
    {
    \coordinate (P\i) at ({60*\i-30}:2cm);
    \draw[\primalstyle] (P0) -- (P\i);
    }
    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
    \begin{scope}[shift={(3cm,0.5cm)}]
        \coordinate (PP0) at (0cm, 0cm);
        \foreach \i in {1,2,...,6}
        {
        \coordinate (PP\i) at ({60*\i-30}:2cm);
        \draw[gray] (PP0) -- (PP\i);
        }
    \end{scope}

@@

    \begin{scope}[shift={(-1.5,-0.25)}]
        \foreach \i in {1,2,...,6}
        {
        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
        }
    \end{scope}
    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
    \draw[blue, ultra thick] (D1) -- (DDD1);
    \draw[blue, ultra thick] (D2) -- (DDD2);
    \draw[blue, ultra thick] (D3) -- (DDD3);
    \draw[blue] (D4) -- (DDD4);
    \draw[blue] (D5) -- (DDD5);
    \draw[blue, ultra thick] (D6) -- (DDD6);

    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);

    \end{tikzpicture}}
    \caption{3D case (2D extrusion)}
    \label{fig:2d-extrusion}
    \end{subfigure}
    \hfill
    \caption{Illustration of primal and dual meshes. (a) A Delaunay-Voronoi grid in 2D (b) The extrusion of 2D mesh. Six triangle prisms are primal cells (depicted by black and gray edges). One dual cell, which is a hexagon prism, is depicted by blue edges. The dashed hexagon represents the intersection of the dual cell and primal cells.}
    \label{fig:illustration_primal_dual}
\end{figure}

@@

\subsubsection{Cut-off Boundary}
In simulations, the meshes are confined by a definite boundary. To make them aligned at boundary, we have to cut off the \emph{dual} elements near the boundary due to the staggered character. In the meantime, extra elements are needed to close $\Tilde{\mathcal{M}}$. These issues are illustrated in Fig. \ref{fig:illustraion_dual_boundary}.

@@

With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be reformulated by a set of algebraic equations:
\begin{center}
\vspace{-0.5cm}
\begin{minipage}{0.3\textwidth}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0,  \\
    \nabla \cdot \mathbf{D} &= \rho, \\
    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
    \mathbf{D} &= \varepsilon \mathbf{E}. 
\end{align*}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\centering
\begin{tikzpicture}
\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align}
    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} , \label{equ:alg_faraday}\\
    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
    \mathbb{D}\mathbf{b} &= \mathbf{0},  \label{equ:alg_gauss_b}\\
    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \label{equ:alg_material_magnetic}\\
    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}, \label{equ:alg_material_electric} 
\end{align}
\end{subequations}
\end{minipage}
\end{center}
where the topping dot $\cdot$ stands for time derivative.

@@

where $\mathbf{p} = (p_i)_i$ denotes the scalar $p$ assigned to each primal vertex in $\Omega_I$ and the matrix $(\mathbb{H})_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}. To incorporate the zero Dirichlet BC, we limit the unknowns $(p_i)_{i=1}^{N^{\Omega^\circ_I}_P}$ to primal vertices in the interior of $\Omega_I$.

@@

The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{F}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variable, $\mathbf{F}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.

To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
\begin{equation} \label{equ:euler_grid} 
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{F}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{F}}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
\end{equation}
where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$. We approximate the analytic flux $\overline{\mathbf{F}}_j$ in (\ref{equ:euler_grid}) by the numerical flux $\overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$. Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p. 44-46]{mishra_2019}. Finally, we end up with the semi-discretized equation:
\begin{equation}
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
    \label{equ:fvm}
\end{equation}
The Rusanov flux in multi-dimensions on face $A_j$ writes
\begin{equation} \label{equ:rusanov-flux-3d}
    \overline{\mathbf{F}}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{F}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{F}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),  
\end{equation}
where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.

We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is strongly connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).

To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$. Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes $|A_i|\overline{\mathbf{F}}_i$, namely $\mathbf{f}_{i,:} = |A_i|\overline{\mathbf{F}}_i$, whose directions are determined by the internal direction of faces where they are defined. In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$. Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P}$ with $\mathbb{\Tilde{V}}_{i,i} = |\Tilde{V}_i|$. Making use of the incidence matrices, we end up with
\begin{equation*}
    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{b},\mathbf{e}),
\end{equation*}
where the dependence of $\mathbf{RHS}$ on $\mathbf{U}, \mathbf{b}, \mathbf{e}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.
\subsubsection{Reconstruction of Lorentz Force}

\subsubsection{Discrete Boundary Conditions}

\subsection{Summary: Spatially Semi-discrete Model}
We collect all the equations and BCs presented above and make a summary for the spatially semi-discrete Maxwell-Euler system:
\begin{subequations}
    \begin{align*}
        [\dot{\mathbf{b}} + \mathbb{C}\mathbf{e} = \mathbf{0}]_i, \ \ &\forall i: A_i \subset \Omega, \\
        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} = - \mathbf{j}]_i, \ \ &\forall i: \Tilde{A}_i \subset \Omega_P,\\
        [\dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} + \mathbb{H} \mathbb{G} \mathbf{p} = - \mathbf{j}]_i, \ \ &\forall i: A_i \subset \Omega_I,\\
        [\Tilde{\mathbb{D}}\mathbf{d} = \mathbf{0}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_I, \\
        [\dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F} = \mathbf{RHS}]_i,\ \ &\forall i: \Tilde{V}_i \subset \Omega_P,
    \end{align*}
with boundary conditions:
    \begin{align*}
    \varphi_i = \Phi^\pm(t), \ \ &\forall i : P_i \subset \Gamma_C^\pm, \\
    e_i = (\mathbb{G}\bm{\varphi})_i,\ \ &\forall i : L_i \subset \partial\Omega, \\
    (\Tilde{\mathbb{C}} \bm{h})_i = 0,\ \ &\forall i : \Tilde{A}_i \subset \Gamma_I,\\
    \mathbf{F}_i = |\Tilde{A}_i|\overline{\mathbf{F}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_C, \\
    \mathbf{F}_i = |\Tilde{A}_i|\overline{\mathbf{F}}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ &\forall i: \Tilde{A}_i \subset \Gamma_W.
    \end{align*}
\end{subequations}

\section{Discretization in time}
\subsection{Motivation: 1D Discretization}
\subsubsection{1D plasma model}
The 3D problem is projected onto the 1D axis by assuming vanishing traverse derivatives (see Fig. \ref{fig:1d-frame} for the definition of reference frame). Besides, $u_y, E_y, B_x, B_z$ are set zero for simplicity, which amounts to considering the TE mode. The collision between particles is omitted for the time being.

>>>>

\newtheorem*{remark}{Remark}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\title{APPM report - Draft}
\author[1]{R. Hiptmair}
\author[1]{T.W. Yu}
\author[2]{R. Fuchs}
\affil[1]{Seminar for Applied Mathematics , ETH Z\"{u}rich}
\affil[2]{IET Institut für Energietechnik, OST}
\date{}

\begin{document}
\maketitle

@@

\section{Spatial Discretization}
\subsection{Primal-dual Staggered Meshes}
\subsubsection{Geometric Property}
Prior to the spatial discretization of the Maxwell-Euler system, we introduce primal-dual staggered meshes that are necessary in the discretization framework we use. The spatial domain is discretized by two meshes that interlace with each other, denoted by a mesh doublet $(\mathcal{M}, \Tilde{\mathcal{M}})$ for primal mesh and dual mesh respectively. The fundamental duality property requires that \emph{each edge of one mesh penetrates a face of the other mesh and that each vertex of one mesh lies at the center of a cell of the other mesh} \citep{weiland_2003}, which makes $(\mathcal{M}, \Tilde{\mathcal{M}})$ staggered. A simple example for Cartesian meshes is shown in Fig. \ref{fig:cartesian}.

@@

The geometrical orthogonality between $L \leftrightarrow \Tilde{A}$ and $A \leftrightarrow \Tilde{L}$ is satisfied and would be a crucial property for approximating the material laws shown in the following section.

@@

\begin{figure}
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \resizebox{0.45\textwidth}{!}{\begin{tikzpicture}
    \def\primalstyle{thick}
    \def\dualstyle{ultra thick}
    \coordinate (P0) at (0cm, 0cm);
    \foreach \i in {1,2,...,6}
    {
    \coordinate (P\i) at ({60*\i-30}:2cm);
    \draw[\primalstyle] (P0) -- (P\i);
    }
    \draw[\primalstyle] (P1) -- (P2) node[above=3mm]{\Large $\mathcal{M}$} node[left=11mm]{\Large \color{blue} $\Tilde{\mathcal{M}}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
    \foreach \i in {1,2,...,6}
    {
    \coordinate (D\i) at ({60*\i-60}:{2./1.737});
    \coordinate (DD\i) at ({60*\i-60}:{4./1.737});
    }
    \draw[blue,\dualstyle] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
    \foreach \i in {1,2,...,6}
    {
    \draw[blue,\dualstyle] (D\i) -- (DD\i);
    }
    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6) -- cycle;
    \end{tikzpicture}}
    \caption{2D case}
    \label{fig:2d-mesh}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \resizebox{0.8\textwidth}{!}{\begin{tikzpicture}
    \def\primalstyle{thick}
    \def\dualstyle{thick}
    \coordinate (P0) at (0cm, 0cm);
    \foreach \i in {1,2,...,6}
    {
    \coordinate (P\i) at ({60*\i-30}:2cm);
    \draw[\primalstyle] (P0) -- (P\i);
    }
    \draw[\primalstyle] (P1) -- (P2) node[left=5mm]{\Large $\mathcal{M}$} -- (P3) -- (P4) -- (P5) -- (P6) -- cycle;
    \begin{scope}[shift={(3cm,0.5cm)}]
        \coordinate (PP0) at (0cm, 0cm);
        \foreach \i in {1,2,...,6}
        {
        \coordinate (PP\i) at ({60*\i-30}:2cm);
        \draw[gray] (PP0) -- (PP\i);
        }
    \end{scope}

@@

    \begin{scope}[shift={(-1.5,-0.25)}]
        \foreach \i in {1,2,...,6}
        {
        \coordinate (DDD\i) at ({60*\i-60}:{2./1.737});
        }
    \end{scope}
    \draw[blue, ultra thick] (DDD1) -- (DDD2) -- (DDD3) node[left=3mm]{\textcolor{blue}{\Large $\Tilde{\mathcal{M}}$}} -- (DDD4) -- (DDD5) -- (DDD6) -- cycle;
    \draw[blue, ultra thick] (D1) -- (DDD1);
    \draw[blue, ultra thick] (D2) -- (DDD2);
    \draw[blue, ultra thick] (D3) -- (DDD3);
    \draw[blue] (D4) -- (DDD4);
    \draw[blue] (D5) -- (DDD5);
    \draw[blue, ultra thick] (D6) -- (DDD6);
    \fill[blue!50, opacity=0.2] (D1) -- (D2) -- (D3) -- (D4) -- (D5) -- (D6);
    \end{tikzpicture}}
    \caption{3D case (2D extrusion)}
    \label{fig:2d-extrusion}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
    \centering
    \begin{tikzpicture}[scale = 0.2]
            \def\style{thick}
            \draw[\style] (0,0) -- (1.5,0);
            \draw[\style] (0,0) -- (0,5) -- (5,5) -- (5,2.5);
            \draw[\style] (0,5) -- (2,7) node[left]{$\mathcal{M}$} -- (7,7) -- (5,5);
            \draw[\style] (7,7) -- (7,3.5);
            \draw[dashed, very thin] (1.5, 0) -- (5,0);
            \draw[dashed, very thin] (5,0) -- (5,2.5);
            \draw[dashed, very thin] (5,0) -- (7,2);
            \draw[dashed, very thin] (7,2) -- (7,3.5);

            \draw[fill = gray!60,\style] (5,2.5) -- (6,3.5) -- (7,3.5) -- (7,7) -- (5,5) -- cycle;
            \draw[fill = gray!10,\style] (0,5) -- (5,5) -- (7,7) -- (2,7) -- cycle;
            \draw[dashed, very thin] (5,0) -- (6.5,1.5) -- (5,1.5) -- cycle;

            \begin{scope}[shift={(1.5,-3.5)}]
            \draw[blue,\style] (0,0) -- (5,0)  node[right]{$\Tilde{\mathcal{M}}$};
            \draw[blue,\style] (5,0) -- (5,5);
            \draw[blue,\style] (5,5) -- (0,5);
            \draw[blue,\style] (0,5) -- (0,0);
            \draw[blue,\style] (0,5) -- (1,6);
            \draw[blue,\style] (4.5,7) -- (7,7);
            \draw[blue,\style] (7,7) -- (5,5);
            \draw[blue,\style] (7,7) -- (7,2);
            \draw[blue,\style] (7,2) -- (5,0);
            \draw[dashed, very thin] (1,6) -- (2,7);
            \draw[dashed, very thin] (2,7) -- (4.5,7);
            \draw[fill = blue!10,\style] (0,5) -- (5,5) -- (7,7) -- (4.5,7) -- (3.5, 6) -- (1,6) -- cycle;
            \draw[fill = blue!40,\style] (5,0) -- (7,2) -- (7,7) -- (5,5) -- cycle;
            \draw[dashed, very thin] (1,6) -- (2,7) -- (3.5,7) -- (3.5,6) -- cycle;
            \end{scope}
        \end{tikzpicture}
        \caption{3D case (Cartesian)}
        \label{fig:cartesian}
    \end{subfigure}
    \hfill
    \caption{Illustration of primal and dual meshes. (a) A Delaunay-Voronoi grid in 2D (b) The extrusion of 2D mesh. Six triangle prisms are primal cells (depicted by black and gray edges). One dual cell, which is a hexagon prism, is depicted by blue edges. The dashed hexagon represents the intersection of the dual cell and primal cells. (c) A Cartesian case.}
    \label{fig:illustration_primal_dual}
\end{figure}

@@

\subsubsection{Cut-off Boundary}
We can only solve problems on a bounded domain and thus the meshes are confined by a definite boundary. To make them aligned at boundary, we have to cut off the \emph{dual} elements near the boundary due to the staggered character. In the meantime, extra elements are needed to close $\Tilde{\mathcal{M}}$. These issues are illustrated in Fig. \ref{fig:illustraion_dual_boundary}.

@@

With the aid of incidence matrices defined in the preceding section and given the discrete material law, (\ref{equ:maxwell_grid_faraday})-(\ref{equ:maxwell_grid_gauss_D}) can be reformulated by a set of algebraic equations:
\begin{center}
\vspace{-0.5cm}
\begin{minipage}{0.3\textwidth}
\begin{align*}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \\
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \\
    \nabla \cdot \mathbf{B} &= 0,  \\
    \nabla \cdot \mathbf{D} &= \rho, \\
    \mathbf{H} &= \mu^{-1} \mathbf{B}, \\
    \mathbf{D} &= \varepsilon \mathbf{E}. 
\end{align*}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\centering
\begin{tikzpicture}
\draw[thick, -{to}] (0,0) -- node[above]{$(\mathcal{M}, \Tilde{\mathcal{M}})$} (1.5,0);
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{subequations}
\begin{align}
    \dot{\mathbf{b}} + \mathbb{C}\mathbf{e} &= \mathbf{0} , \label{equ:alg_faraday}\\
    \dot{\mathbf{d}} - \Tilde{\mathbb{C}}\mathbf{h} &= - \mathbf{j}, \label{equ:alg_empere}\\
    \mathbb{D}\mathbf{b} &= \mathbf{0},  \label{equ:alg_gauss_b}\\
    \Tilde{\mathbb{D}}\mathbf{d} &= \mathbf{q},  \label{equ:alg_gauss_d}\\
    \mathbf{h} &= \mathbb{M}_\mu^{-1} \mathbf{b}, \label{equ:alg_material_magnetic}\\
    \mathbf{d} &= \mathbb{M}_{\varepsilon} \mathbf{e}, \label{equ:alg_material_electric} 
\end{align}
\end{subequations}
\end{minipage}
\end{center}
where the topping dot $\cdot$ stands for taking time derivative.

@@

where $\mathbf{p} = (p_i)_i$ denotes the scalar $p$ assigned to each primal vertex in $\Omega_I$ and the matrix $\mathbb{H}_{i,i} = \frac{|\Tilde{A}_i|}{|L_i|}$ transforms primal edge integrals to dual face fluxes\footnote{$\mathbb{H}$ functions as a discrete Hodge operator.}. To incorporate the zero Dirichlet BC, we limit the unknowns $(p_i)_{i=1}^{N^{\Omega^\circ_I}_P}$ to primal vertices in the interior of $\Omega_I$.

@@

The Euler equations (\ref{equ:euler_}) can be generalized into the form of conservation law with source terms:
\begin{equation} \label{equ:euler_conservation}
    \partial_t \mathbf{U} + \nabla \cdot \mathbf{f}(\mathbf{U}) = \mathbf{RHS},
\end{equation}
where $\mathbf{U} \in L^2(\Omega \times [0,T], \mathbb{R}^m)$ stands for $m$ conservative variable, $\mathbf{f}(\mathbf{U}) \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the flux density, and $\mathbf{RHS} \in L^2(\Omega \times  [0,T], \mathbb{R}^m)$ is the source term.

To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
\begin{equation} \label{equ:euler_grid} 
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{\overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{\overline{\mathbf{RHS}}_i}
\end{equation}
where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ calculates the cell average, $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$. We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$. Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p. 44-46]{mishra_2019}. Finally, we end up with the semi-discretized equation:
\begin{equation}
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
    \label{equ:fvm}
\end{equation}
The Rusanov flux in multi-dimensions on face $A_j$ writes
\begin{equation} \label{equ:rusanov-flux-3d}
    \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{f}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{f}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),  
\end{equation}
where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.

We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).

To rewrite (\ref{equ:fvm}) into a matrix form, by abuse of notation we stack all the cell average $(\overline{\mathbf{U}}_i)_i$ into a matrix $\mathbf{U} \in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ with $\mathbf{U}_{i,:} = \overline{\mathbf{U}}_i$. Meanwhile, we denote by $\mathbf{F} \in \mathbb{R}^{N_{\Tilde{A}}^P \times m}$ the collection of the (total) numerical fluxes, namely $\mathbf{F}_{i,:} = |A_i|\mathbf{f}^\text{num}_i$. In the same way, we denote by $\mathbf{RHS}\in \mathbb{R}^{N_{\Tilde{V}}^P \times m}$ the collection of $\overline{\mathbf{RHS}}_i$. Besides, we define the diagonal matrix $\mathbb{\Tilde{V}} \in \mathbb{R}^{N_{\Tilde{V}}^P}$ with $\mathbb{\Tilde{V}}_{i,i} = |\Tilde{V}_i|$. Making use of the incidence matrices, we end up with
\begin{equation*}
    \dot{\mathbf{U}} + \mathbb{\Tilde{V}}^{-1}\mathbb{\Tilde{D}}\mathbf{F}(\mathbf{U})  = \mathbf{RHS}(\mathbf{U},\mathbf{d},\mathbf{b}),
\end{equation*}
where the dependence of $\mathbf{RHS}$ on $\mathbf{U}, \mathbf{d}, \mathbf{b}$ is implied by (\ref{equ:euler_rescaled}) and will be elaborated below.

\subsubsection{Reconstruction of Lorentz Force}
Since the electromagnetic fields are represented by integrals on edges and faces, we need to reconstruct their vector components for the computation of Lorentz force (and Joule heating) inside each dual volume.

The problem is twofold:
\begin{itemize}
    \item[-] given the fluxes at faces of a volume, reconstruct the vector field inside the volume;
    \item[-] given the integrals along edges of a volume, reconstruct the vector field inside the volume. 
\end{itemize}
We adopt the principle of least square fitting, and reconstruct a \emph{constant} vector field inside each volume. For a volume $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying 
\begin{equation*}
    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{v} \cdot \mathbf{n}_i - f_i)^2.   
\end{equation*} can be computed through
\begin{equation*}
    \mathbf{v} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
\end{equation*}
where
\begin{equation*}
    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
\end{equation*}
and each vector in $\mathbb{R}^3$ is treated as a column vector. The construction based on the integral quantities on edges can be done similarly. Assembling the local constructions for each dual volume, the global construction can be written as 
\begin{equation}
    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d},
    \ \ \ \ 
    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b},
\end{equation}
where $\mathbf{d}, \mathbf{b}$ are stacked unknowns, see Tab. \ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.

The problem of the reconstruction of vector fields on unstructured meshes is a widely studied topic. Apart from the least-square method, other methods include Perot's method \citep{perot_2000}, finite-element-based methods, etc., which potentially can achieve higher-order accuracy. See \cite[][sec. 3.4.4]{fuchs_2021} and the references therein.
